Paper

### 2018-03-08 Paper.Rmd
...

gp = globalCN.plot + theme(legend.position = 'none') + labs(y='mean adj. seg.', title='All samples') + theme(text=element_text(size=12))
ggsave(filename='plots/globalCN.png', plot=gp, width=16, height=4.6, units='in', dpi=300)

gbe = globalBECN.plot + theme(legend.position = 'none') + labs(y='mean adj.seg.', title="Non-Dysplastic Barrett's Samples") + theme(text=element_text(size=12))
ggsave(filename='plots/globalBECN.png', plot=gbe, width=16, height=4.6, units='in', dpi=300)

@@

>>>>

gp = globalCN.plot + theme(legend.position = 'none') + labs(y='mean adj. seg.', title='All samples')# + theme(text=element_text(size=12))
ggsave(filename='plots/globalCN.png', plot=gp, width=16, height=4.6, units='in', dpi=300)

gbe = globalBECN.plot + theme(legend.position = 'none') + labs(y='mean adj.seg.', title="Non-Dysplastic Barrett's Samples") 
ggsave(filename='plots/globalBECN.png', plot=gbe, width=16, height=4.6, units='in', dpi=300)

@@

ggplot(back, aes(Status, OR, color=OR)) + 
  geom_boxplot(outlier.colour=NA) + geom_jitter(width=0.3, aes(shape=Pathology)) + 
  scale_color_gradientn(colors = myPal,  name='') + plot.theme
